Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2018-01-24 writeup/conStruct.tex
minor edits to LD section

\gb{If the spatial coordinates of the loci in the genome are known, 
the training/testing partitioning should be designed to accommodate linkage disequilibrium (LD).
Loci in strong LD do not represent independent instantiations of the coalescent process, 
so if loci from a single linkage block are randomly split into both training and testing partitions, 
the independence of the test in the testing partition will be compromised 
(e.g., the parameters estimated from the training partition 
might be describing process heterogeneity or noise 
in a region of the genome that also has loci included in the testing partition).
If genomic position or LD between SNPs is known, 
the best practice for cross-validation is to make sure that 
no loci in the testing dataset are in strong LD with, 
or spatially proximate to, loci in the testing dataset.}

>>>>

If the genomic coordinates of the loci are known, 
the training/testing partitioning should be designed to accommodate linkage disequilibrium (LD).
Loci in strong LD are not inherited independently,
so if loci from a single linkage block are included in both training and testing partitions, 
the independence of the test in the testing partition will be compromised,
and so the parameters estimated from the training partition 
might be describing process heterogeneity or noise 
in a region of the genome that also has loci included in the testing partition.
The best practice for cross-validation is to make sure that 
no loci in the testing dataset are in strong LD with, 
or near to on the genome, loci in the testing dataset.
